\section{STAKEHOLDER REQUIREMENTS} 

%list of stakeholders considered
% 1. The design students
% 2. Dr. Cripps and Joelyn
% 3. UAS hobbyists(end user in theory)
% 4. DOD(alternate theoretical end user)

\subsection{Physical}
\begin{enumerate}
    \item The device must fit inside of a typical RC airplane. 
    \item The flight controller must be battery powered.
    \item The device must have ports commonly used for connecting parts used in flight.
\end{enumerate}

\subsection{Behaviorial}
\begin{enumerate}
    \item The flight controller must keep stable drone flight during operation.
    \item The flight controller must handle autonomous flight as well as teleoperated flight.
    \item Regardless of control method, the flight controller must avoid the plane losing stability or crashing.
    \item The flight controller must be able to be configured with the parameters of a given plane.
\end{enumerate}

\subsection{Functional}
\begin{enumerate}
    \item The flight controller must provide proper inputs to the control surfaces of the drone.
    \item The flight controller must accept a programmed mission plan for autonomous flight.
    \item The flight controller must read from on board sensors in order to provide stable controls to the plane.
    \item The flight controller must allow for additional sensors to be connected.
\end{enumerate}

\subsection{Environmental}
\begin{enumerate}
    \item The flight controller must be able to operate during potentially rough flight of a small airplane.
    \item The flight controller must work the same even when the tempurature or air pressure changes.
    \item The flight controller must be able to function regardless of vibrations from the plane.
\end{enumerate}

\subsection{Ethical}
\begin{enumerate}
    \item The flight controller must have safety checks to ensure sufficient power at least 5 minutes of flight.
    \item In the event of a failure the flight controller must attempt to land safely instead of simply crashing.
    \item The system must report and log failures of flight components.
\end{enumerate}